Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion

### 2017-02-12 Submission_2016_source/submission.tex
Updates

\documentclass[10pt,letterpaper]{article}
\usepackage{opex3}
\usepackage{color}
\usepackage{amsmath}
%%%%%%%%%%%%%%%%%%%%%
% REMOVE BEFORE SUBMISSION
\usepackage{amsmath,amssymb,graphicx}
\usepackage{dcolumn}%
\usepackage{array,multirow}
\usepackage{bm}%
\usepackage{cite}
\usepackage{pstool}%
\usepackage{array}
\usepackage{xcolor}
\usepackage{subcaption,subfloat} % lets you have multiple pictures next to each other
%%\usepackage{upgreek}
%\usepackage[numbers,sort&compress]{natbib}
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{A\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{A\arabic{figure}}%
     }

\begin{document}

\title{Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion } %Title of paper

\author{Mool C. Gupta,$^1$ Craig Ungaro,$^1$ 
Jonathan J. Foley IV,$^{2,3}$ and Stephen K. Gray$^2$}

\address{$^1$Department of Electrical \& Computer Engineering, University of Virginia, Charlottesville, Virginia, 22901, USA \\
$^2$Center for Nanoscale Materials, Argonne National Laboratory, 9700 South Cass Avenue, Argonne, IL, 60439, USA \\
$^3$Department of Chemistry, William Paterson University, 300 Pompton Road, Wayne, NJ, 07470, USA \\
$^1$mgupta@virginia.edu \\
$^2$gray@anl.gov}

@@

%\ocis{350.6050}% REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE
%                          % NOTE: \ocis{} IS ALIASED TO \pacs{} BUT MUST
%                          % FORMAT THE TERMS CORRECTLY FOR EACH JOURNAL
\ocis{(220.022) Optical design and fabrication; (230.023) Optical devices;  (240.024) Optics at surfaces; (240.031) Thin films; (350.605) Solar Energy; (310.662) Subwavelength structures, nanostructures.}
%%%\maketitle %% required

\bibliographystyle{osajnl}

\providecommand{\noopsort}[1]{}\providecommand{\singleletter}[1]{#1}%
\begin{thebibliography}{100}
\newcommand{\enquote}[1]{``#1''}

\bibitem{g1}
M.~Thirugnanasambandam, S.~Iniyan, and R.~Goic, \enquote{A review of solar
  thermal technologies,} Renewable and Sustainable Energy Reviews \textbf{14},
  312--322 (2010).

\bibitem{g2}
Y.~Tian and C.~Y. Zhao, \enquote{A review of solar collectors and thermal
  energy storage in solar thermal applications,} Applied Energy \textbf{104},
  538--553 (2013).

\bibitem{g3}
T.~Bauer, \emph{Thermophotovoltaics: basic principles and critical aspects of
  system design} (Springer, 2011).

\bibitem{g4}
P.~Bermel, M.~Ghebrebrhan, W.~Chan, Y.~X. Yeng, M.~Araghchini, R.~Hamam, C.~H.
  Marton, K.~F. Jensen, M.~Soljacic, J.~D. Joannopoulos, S.~G. Johnson, and
  I.~Celanovic, \enquote{Design and global optimization of high-efficiency
  thermophotovoltaic systems,} Opt. Express \textbf{18}, A314--334 (2010).

\bibitem{g5}
N.~Harder and P.~Wurfel, \enquote{Theoretical limits of thermophotovoltaic
  solar energy conversion,} Semiconductor Science and Technology \textbf{18},
  S151 (2003).

\bibitem{g6}
C.~Ferrari, F.~Melino, M.~Pinelli, P.~R. Spina, and M.~Venturini,
  \enquote{Overview and status of thermophotovoltaic systems,} Energy Procedia
  \textbf{45}, 1160--1169 (2014).

\bibitem{g7}
P.~Bermel, J.~Lee, J.~D. Joannopoulos, I.~Celanovic, and M.~Soljacie,
  \emph{Selective Solar Absorbers} (Begell House Inc., 2012), chap.~7, Annual
  Review of Heat Transfer.

\bibitem{g8}
T.~Inoue, M.~Zoysa, T.~Asano, and S.~Noda, \enquote{Realization of narrowband
  thermal emission with optical nanostructures,} Optica \textbf{2}, 27 (2015).

\bibitem{g9}
A.~Lenert, D.~M. Bierman, Y.~Nam, W.~R. Chan, I.~Celanovic, M.~Soljacic, and
  E.~N. Wang, \enquote{A nanophotonic solar thermophotovoltaic device,} Nat.
  Nanotechnol. \textbf{9}, 126--130 (2014).

\bibitem{RF_OptExp_2009}
E.~Rephaeli and S.~Fan, \enquote{Absorber and emitter for solar
  thermophotovoltaic systems to achieve efficiency exceeding the
  schockley-queisser limit,} Opt. Express \textbf{17}, 15145--15159 (2009).

\bibitem{G_PS_1985}
C.~G. Granqvist, \enquote{Spectrally selective coatings for energy efficiency
  and solar applications,} Phys. Scripta \textbf{32}, 401 (1985).

\bibitem{C_RPP_2014}
S.~Collin, \enquote{Nanostructure arrays in free space: optical properties and
  applications,} Rep. Prog. Phys. \textbf{77}, 126402 (2014).

\bibitem{g11}
V.~Rinnerbauer, A.~Lenert, D.~M. Bierman, Y.~X. Yeng, W.~R. Chan, R.~D. Geil,
  J.~J. Senkevich\, J.~D. Joannopoulos, E.~N. Wang, M.~Soljacic, and
  I.~Cleanovic, \enquote{{Metallic photonic crystal absorber-emitter for
  efficient spectral control in high-temperature solar thermophotovoltaics},}
  Advanced Energy Materials \textbf{4}, 1400334 (2014).

\bibitem{NYL_SEMSC_2014}
Y.~Nam, Y.~X. Yeng, A.~Lenert, P.~Bermel, I.~Celanovic, M.~Solja\v{c}i\'{c},
  and E.~N. Wang, \enquote{Solar thermophotovoltaic energy conversion systems
  with two-dimensional tantalum photonic crystal absorbers and emitters,} Sol.
  Energy Mat. Sol. Cells \textbf{122}, 287 -- 296 (2014).

\bibitem{g13}
V.~Stelmakh, V.~Rinnerbauer, W.~R. Chan, J.~J. Senkevich, J.~D. Joannopoulos,
  M.~Soljacic, and I.~Celanovic, \enquote{Tantalum-tungsten alloy photonic
  crystals for high-temperature energy conversion systems,} Proceedings of the
  SPIE - The International Society for Optical Engineering \textbf{9127},
  91270Q (2014).

\bibitem{g14}
I.~Celanovic, N.~Jovanovic, and J.~Kassakian, \enquote{Two-dimensional tungsten
  photonic crystals as selective thermal emitters,} Appl. Phys. Lett.
  \textbf{92}, 193101 (2008).

\bibitem{g15}
H.~Wang, V.~P. Sivan, A.~Mitchell, G.~Rosengarten, P.~Phelan, and L.~Wan,
  \enquote{Highly efficient selective metamaterial absorber for
  high-temperature solar thermal energy harvesting,} Sol. Energy Mat. Sol.
  Cells \textbf{137}, 235--242 (2015).

\bibitem{g16}
X.~Liu, T.~Tyler, T.~Starr, A.~Starr, N.~Jokerst, and W.~Padilla,
  \enquote{Taming the blackbody with infrared metamaterials as selective
  thermal emitters,} Phys. Rev. Lett. \textbf{107}, 045901 (2011).

\bibitem{g17}
I.~Khodasevvch, L.~Wang, A.~Mitchell, and G.~Rosengarten, \enquote{Micro and
  nanostructured surfaces for selective solar absorption,} Adv. Opt. Mater.
  \textbf{107}, 045901 (2015). {doi: 10.1002/adom.201500063}.

\bibitem{g18}
Y.~Son, J.~Yeo, C.~Woo, H.~Sukjoon, H.~Seung, H.~Ko, and D.~Yang,
  \enquote{Fabrication of submicron-sized metal patterns on a flexible polymer
  substrate by femtosecond laser sintering of metal nanoparticles,}
  International Journal of Nanomanufacturing \textbf{9}, 468--476 (2013).

\bibitem{g19}
E.~P.~B. Filho, O.~S.~H. Mendoza, C.~L.~L. Beicker, A.~Menezes, and D.~Wen,
  \enquote{Experimental investigation of a silver nanoparticle-based direct
  absorption solar thermal system,} Energy Conversion and Management
  \textbf{84}, 261--267 (2014).

\bibitem{g20}
G.~Katumba, L.~Olumekor, A.~Forbes, G.~Makiwa, B.~Mwakikunga, J.~Lu, and
  E.~Wackelgard, \enquote{Optical, thermal and structural characteristics of
  carbon nanoparticles embedded in {Z}n{O} and {N}i{O} as selective solar
  absorbers,} Sol. Energy Mater. and Solar Cells \textbf{92}, 1285--1292
  (2008).

\bibitem{g21}
A.~A. Shah and M.~C. Gupta, \enquote{Spectral selective surfaces for
  concentrated solar power receivers by laser sintering of tungsten micro and
  nano particles,} Sol. Energy Mat. Sol. Cells \textbf{117}, 489--493 (2013).

\bibitem{g22}
J.~H. Schon, G.~Binder, and E.~Bucher, \enquote{Performance and stability of
  some new high-temperature selective absorber systems based on
  metal/dielectric multilayers,} Sol. Energy Mat. Sol. Cells \textbf{33},
  403--416 (1994).

\bibitem{g25}
V.~K. Narasimhan and Y.~Cui, \enquote{Nanostructures for photon management in
  solar cells,} Nanophotonics \textbf{2}, 187–210 (2013).

\bibitem{g26}
M.~C. Gupta, B.~K. Nayak, V.~Iyengar, and L.Wang, \enquote{Efficient light
  trapping by laser microtexturing of surfaces for photovoltaics,} SPIE
  Newsroom  (2012). DOI: 10.1117/2.1201208.004361.

\bibitem{g27}
M.~C. Gupta and D.~E. Carlson, \enquote{Laser processing for renewable energy
  materials,} MRS Energy and Sustainability: A Review Journal  (2015).
  DOI:10.1557/mre.2015.3.

\bibitem{g28}
V.~V. Iyengar, B.~K. Nayak, and M.~C. Gupta, \enquote{Ultralow reflectance
  metal surfaces by ultrafast laser texturing,} Appl. Opt. \textbf{49},
  5983--5988 (2010).

\bibitem{L_AIP_2007}
A.~Luque, \enquote{Solar thermophotovoltaics: Combining solar thermal and
  photovoltaics,} AIP Conf. Proc. \textbf{890}, 3--16 (2007).

\bibitem{RKR_RenEnRev_2013}
V.~S. Reddy, S.~C. Kaushik, K.~R. Ranjan, and S.~K. Tyagi,
  \enquote{State-of-the-art of solar thermal power plants-a review,} Renew.
  Sust. Energ. Rev. \textbf{27}, 258--273 (2013).

\bibitem{MS_EnConvMan_2012}
R.~K. McGovern and W.~J. Smith, \enquote{Optimal concentration and temperatures
  of solar thermal power plants,} Energ. Convers. Manage. \textbf{60}, 226--232
  (2012).

\bibitem{global_opt}
A.~Datas and C.~Algora, \enquote{Global optimization of solar
  thermophotovoltaic systems,} Progress in Photovoltaics: Research and
  Applications \textbf{21}, 1040--1055 (2013).

\bibitem{paper2_ref6}
Y.~Xuan, X.~Chen, and Y.~Han, \enquote{Design and analysis of
  thermophotovoltaic systems,} Renew. Energ. \textbf{36}, 374--387 (2011).

\bibitem{paper1_ref5}
K.~A. Arpin, M.~D. Losego, and P.~V. Braun, \enquote{{Electrodeposited 3D
  tungsten photonic crystals with enhanced thermal stability},} Chemistry of
  Materials \textbf{23}, 4783--4788 (2011).

\bibitem{me1}
C.~Ungaro, S.~K. Gray, and M.~C. Gupta, \enquote{Black tungsten for solar power
  generation,} Appl. Phys. Lett. \textbf{103}, 071105--071105--3 (2013).

\bibitem{paper1_ref6}
H.~Sai and H.~Yugami, \enquote{Thermophotovoltaic generation with selective
  radiators based on tungsten surface gratings,} Appl. Phys. Lett. \textbf{85},
  3399--3401 (2004).

\bibitem{paper2_ref13}
H.~Sai, Y.~Kanamori, K.~Hane, H.~Yugami, and M.~Yamaguchi, \enquote{Numerical
  study on tungsten selective radiators with various micro/nano structures,}
  Photovoltaic Specialists Conference pp. 762--765 (2005).

\bibitem{paper2_ref14}
Y.~B. Chen and Z.~M. Zhang, \enquote{Design of tungsten complex gratings for
  thermophotovoltaic radiators,} Opt. Comm. \textbf{269}, 411--417 (2007).

\bibitem{Grann_JOSA}
E.~B. Grann and M.~G. Moharam, \enquote{Comparison between continuous and
  discrete subwavelength grating structures for antireflection surfaces,} J.
  Opt. Soc. Am. \textbf{13}, 988--922 (1996).

\bibitem{me2}
C.~Ungaro, S.~K. Gray, and M.~C. Gupta, \enquote{Graded-index structures for
  high-efficiency solar thermophotovoltaic emitting surfaces,} Opt. Lett.
  \textbf{39}, 5259--5262 (2014).

\bibitem{G_JPCC_2013}
S.~K. Gray, \enquote{Theory and modeling of plasmonic structures,} J. Phys.
  Chem. C \textbf{117}, 1983--1994 (2013).

\bibitem{Taflove_FDTD}
A.~Taflove and S.~C. Hagness, \emph{Computational Electrodynamics: the
  Finite-Difference Time-Domain Method} (Artech, 2000).

\bibitem{Meep}
A.~F. Oskooi, D.~Roundy, M.~Ibanescu, P.~Bermel, J.~D. Joannopoulos, and S.~G.
  Johnson, \enquote{Meep: A flexible free-software package for electromagnetic
  simulations by the {FDTD} method,} Comp. Phys. Comm. \textbf{181}, 687–702
  (2010).

\bibitem{Bohren}
C.~F. Bohren and D.~R. Huffman, \emph{Absorption and Scattering of Light by
  Small Particles} (John Wiley and Sons, 1998).

\bibitem{Yeh}
P.~Yeh, \emph{Optical Waves in Layered Media} (Wiley, 2005).

\bibitem{DF_JOptSocA_1994}
B.~T. Draine and P.~J. Flatau, \enquote{Discrete-dipole approximation for
  scattering calculations,} J. Opt. Soc. Am. A \textbf{11}, 1491--1499 (1994).

\bibitem{fem}
J.~M. McMahon, \enquote{Topics in theoretical and computational nanoscience:
  From controlling light at the nanoscale to calculating quantum effects with
  classical electrodynamics,} Ph.D. thesis, Northwestern University (2011).

\bibitem{RCWA1}
M.~G. Moharam, D.~A. Pommet, E.~B. Grann, and T.~K. Gaylor, \enquote{Stable
  implementation of the rigorous coupled-wave analysis for surface-relief
  gratings: enhanced transmittance matrix approach,} J. Opt. Soc. A
  \textbf{12}, 1077 (1995).

\bibitem{RCWA2}
L.-L. Lin, Z.-Y. Li, and K.-M. Ho, \enquote{Lattice symmetry applied in
  transfer-matrix methods for photonic crystals,} J. Appl. Phys. \textbf{98},
  811 (2003).

\bibitem{A13}
H.~Saia, H.~Yugamia, Y.~Kanamorib, and K.~Hane, \enquote{Solar selective
  absorbers based on two-dimensional {W} surface gratings with submicron
  periods for high-temperature photothermal conversion,} Sol. Energy Mat. Sol.
  Cells \textbf{79}, 35--49 (2003).

\bibitem{RCWA3}
V.~Rinnerbauer, Y.~Shen, J.~D. Joannopolous, M.~Solja{\v c}i{\' c}, F.~Sch{\"
  a}ffler, and I.~Celanovic, \enquote{Superlattice photonic crystal as
  broadband solar absorber for high temperature operation,} Opt. Express
  \textbf{22}, A1895 (2014).

\bibitem{BCM_PRB_1988}
R.~G. Barrerra, M.~{del Castillo-Mussot}, G.~Monsivais, P.~Villaseor, and W.~L.
  Moch\'{a}n, \enquote{Optical properties of two-dimensional disordered systems
  on a substrate,} Phys. Rev. B \textbf{38}, 5371 (1988).

\bibitem{BMM_PRB_1991}
R.~G. Barrerra, G.~Monsivais, and W.~L. Moch\'{a}n, \enquote{Renormalized
  polarizability in the maxwel garnett theory,} Phys. Rev. B \textbf{43}, 13819
  (1991).

\bibitem{YP_OptExpress_2012}
S.~Yoo and Q.-H. Park, \enquote{Effective permittivity for resonant plasmonic
  nanoparticle systems via dressed polarizability,} Opt. Express \textbf{20},
  16480 (2012).

\bibitem{AP_NatMat_2010}
H.~A. Atwater and A.~Polman, \enquote{Plasmonics for improved photovoltaic
  devices,} Nature Mater. \textbf{9}, 205--213 (2010).

\bibitem{GGG_NatComm_2012}
J.~M. Geffrin, B.~Garc\'{i}a-C\'{a}mara, R.~G\'{o}omez-Medina, P.~Albella,
  L.~S. Froufe-P\'{e}rez, C.~Eyraud, A.~Litman, R.~Vaillon, F.~Gonz\'{a}lez,
  M.~Nieto-Vesperinas, J.~J. S\'{a}enz, and F.~Moreno, \enquote{Magnetic and
  electric coherence in forward- and back-scattered electromagnetic waves by a
  single dielectric subwavelength sphere,} Nat. Commun. \textbf{3}, 1171
  (2012).

\bibitem{CH_APL_2006}
J.~R. Cole and N.~J. Halas, \enquote{Optimized plasmonic nanoparticle
  distributions for solar spectrum harvesting,} Appl. Phys. Lett. \textbf{89},
  153120 (2006).

\bibitem{FKA_OptExp_2014}
K.~T. Fountaine, C.~G. Kendall, and H.~A. Atwater, \enquote{Near-unity
  broadband absorption designs for semiconducting nanowire arrays via localized
  radial mode excitation,} Opt. Express \textbf{22}, A930 (2014).

\bibitem{SVP_NatComm_2012}
P.~Spinelli, M.~A. Verschuuren, and A.~Polman, \enquote{Broadband
  omnidirectional antireflection coating based on subwavelength surface {M}ie
  resonators,} Nat. Commun. \textbf{3}, 692 (2012).

\bibitem{paper1_ref4}
E.~Rephaeli and S.~Fan, \enquote{Tungsten black absorber for solar light with
  wide angular operation range,} Appl. Phys. Lett. \textbf{92}, 211107 (2008).

\bibitem{BN_JApplPhys_2005}
P.~Ben-Adballah and B.~Ni, \enquote{Single-defect bragg stacks for high-power
  narrow-band thermal emission,} J. Appl. Phys \textbf{97}, 104910 (2005).

\bibitem{LZ_JApplPhys_2006}
B.~J. Lee and Z.~M. Zhang, \enquote{Design and fabrication of planar multilayer
  structures with coherent thermal emission characteristics,} J. Appl. Phys
  \textbf{100}, 063529 (2006).

\bibitem{FUS_OptExp_2015}
J.~J. {Foley IV}, C.~Ungaro, K.~Sun, M.~C. Gupta, and S.~K. Gray,
  \enquote{Design of emitter structures based on resonant perfect absorption
  for thermophotovoltaic applications,} Opt. Express \textbf{23}, A1373 (2015).

\bibitem{FMS_ACSPhoton_2014}
J.~J. {Foley IV}, J.~M. McMahon, G.~C. Schatz., H.~Harutyunyan, G.~P.
  Wiederrecht, and S.~K. Gray, \enquote{Inhomogeneous surface plasmon
  polaritons,} ACS Photonics \textbf{1}, 739--745 (2014).

\bibitem{CWH_JQSRT_2005}
P.~C. Chang, J.~G. Walker, and K.~I. Hopcraft, \enquote{Ray tracing in
  absorbing media,} J. Quant. Spectrosc. Radiat. Transfer \textbf{96}, 327--341
  (2005).

\bibitem{WH_PSSb_1987}
L.~Wendler and R.~Haupt, \enquote{An improved virtual mode theory of {ATR}
  experiments of surface polaritons,} Phys. Stat. Sol. b \textbf{143}, 131--147
  (1987).

\bibitem{Maier}
S.~M. Maier, \emph{Plasmonics: Fundamentals and Applications} (Springer, 2007).

\bibitem{Novotny}
L.~Novotny and B.~Hecht, \emph{Principles of Nano-Optics} (Cambridge
  University, 2012), 2nd ed.

\bibitem{FHR_SciRep_2015}
J.~J. {Foley IV}, H.~Harutyunyan, D.~Rosenmann, R.~Divan, G.~P. Wiederrecht,
  and S.~K. Gray, \enquote{When are surface plasmon polaritons excited in the
  {K}retschmann-{R}aether configuration?} Sci. Rep. \textbf{5}, 09929 (2015).

\bibitem{DD_APL_2009}
E.~F.~C. Driessen and M.~J.~A. de~Dood, \enquote{The perfect absorber,} Appl.
  Phys. Lett. \textbf{94}, 171109 (2009).

\bibitem{KSL_APL_2012}
M.~A. Kats, D.~Sharma, J.~Lin, P.~Genevet, R.~Blanchard, Z.~Yang, M.~M.
  Qazilbash, D.~N. Basov, S.~Ramanathan, and F.~Capasso, \enquote{Ultra-thin
  perfect absorber employing a tunable phase change material,} App. Phys. Lett.
  \textbf{101}, 221101 (2012).

\bibitem{KBG_NatMat_2013}
M.~A. Kats, R.~Blachard, P.~Genevet, and F.~Capasso, \enquote{Nanometer optical
  coatings based on strong interference effects in highly absorbing media,}
  Nat. Mat. \textbf{12}, 20--24 (2013).

\bibitem{Raether}
H.~Raether, \emph{Surface Plasmons on Smooth and Rough Surfaces and on
  Gratings} (Springer-Verlag, 1988).

\bibitem{DB_JApplPhys_2007}
J.~Drevillon and P.~Ben-Abdallah, \enquote{{\it Ab initio} design of coherent
  thermal sources,} J. Appl. Phys. \textbf{102}, 114305 (2007).

\bibitem{NDJ_JApplPhys_2012}
E.~Nefzaoui, J.~Drevillon, and K.~Joulain, \enquote{Selective emitters design
  and optimization for thermophotovoltaic applications,} J. Appl. Phys.
  \textbf{111}, 084316 (2012).

\bibitem{SKY_JPE_2015}
M.~Shimizu, A.~Kohiyama, and H.~Y. Yugami, \enquote{High-efficiency
  solar-thermophotovoltaic system equipped with a monolithic planar selective
  absorber/emitter,} J. Photon. Energy \textbf{5}, 053099--53107 (2015).

\bibitem{rodriguez2011}
A.~W. Rodriguez, O.~Ilic, P.~Bermel, I.~Celanovic, J.~D. Joannopoulos,
  M.~Soljacic, and S.~G. Johnson, \enquote{Frequency-selective near-field
  radiative heat transfer between photonic crystal slabs: A computational
  approach for arbitrary geometries and materials,} Phys. Rev. Lett.
  \textbf{107}, 114302 (2011).

\bibitem{datas2013}
A.~Datas, D.~Hirashima, and K.~Hanamura, \enquote{{FDTD} simulation of
  near-field radiative heat tansfer between thin films supporting surface
  phonon polaritons: Lessons learned,} J. Therm. Sci. Tech. \textbf{8}, 91--105
  (2013).

\bibitem{didari2014}
A.~Didari and M.~P. Menguc, \enquote{Analysis of near-field radiation transfer
  within nano-gaps using {FDTD} method,} J. Quant. Spect. Radiat. Transf.
  \textbf{146}, 214--226 (2014).

\bibitem{didari2015}
A.~Didari and M.~P. Menguc, \enquote{Near-field thermal emission between
  corrugated surfaces separated by nano-gaps,} J. Quant. Spect. Radiat. Transf.
  \textbf{158}, 43--51 (2015).

\bibitem{AFB_NatComm_2011}
K.~Aydin, V.~E. Ferry, R.~M. Briggs, and H.~A. Atwater, \enquote{Broadband
  polarization-independent resonant light absorption using ultrathin plasmonic
  super absorbers,} Nature Comm. \textbf{2}, 517 (2011).

\bibitem{lumerical}
{Lumerical Solutions, Inc.},
  \url{http://www.lumerical.com/tcad-products/mode/}.
\bibitem{YMH_PRE_2010}
M.~A. Yurkin, M.~Min, and A.~G. Hoekstra, \enquote{Applicaton of the discrete
  dipole approximation to very large refractive indices: Filtered doupled
  dipoles revived,} Phys. Rev. E \textbf{82}, 036703 (2010).

\bibitem{loke2010}
V.~L.~Y. Loke and M.~P. Menguc, \enquote{Surface waves and atomic force
  microscope probe-particle near-field coupling: discrete dipole approximation
  with surface interaction,} J. Opt. Soc. Am. A \textbf{27}, 2293--2303 (2010).

\bibitem{edalatpour2014}
S.~Edalatpour and M.~Francoeur, \enquote{The thermal discrete dipole
  approximation (t-dda) for near-field radiative heat transfer simulations in
  three-dimensional arbitrary geometries,} J. Quant. Spect. Radiat. Transf.
  \textbf{133}, 364--373 (2015).

\bibitem{Simplex}
J.~A. Nelder and R.~Mead, \enquote{A simplex method for function minimization,}
  Comp. J. \textbf{7}, 308--313 (1965).

\bibitem{ga}
A.~Lin and J.~Phillips, \enquote{Optimization of random diffraction gratings in
  thin-film solar cells using genetic algorithms,} Sol. Energy Mat. Sol. Cells
  \textbf{92}, 1689--1696 (2008).

\bibitem{ParticleSwarm}
M.~Clerc, \emph{Particle Swarm Optimization} (Wiley, 2008).

\bibitem{miller1}
R.~L. Miller, Z.~Xie, S.~Leyffer, M.~J. Davis, and S.~K. Gray,
  \enquote{Surrogate-based modeling of the optical response of metallic
  nanostructures,} J. Phys. Chem. C \textbf{114}, 20741--20748 (2010).

\bibitem{g29}
V.~V. Iyengar, B.~K. Nayak, and M.~C. Gupta, \enquote{Optical characteristics
  of femtosecond laser micromachined periodic structures in {S}i 100,} Appl.
  Opt. \textbf{45}, 7137--7143 (2006).

\bibitem{g30}
M.~C. Gupta and S.~T. Peng, \enquote{Diffraction characteristics of
  surface-relief gratings,} Appl. Opt. \textbf{32}, 2911--2917 (1993).

\bibitem{LaserProcessing}
W.~M. Steen and J.~Mazumder, \emph{Laser Material Processing} (Springer, 2010),
  4th ed.

\bibitem{GlancingAngle}
M.~M. Hawkeye, M.~T. Tashuk, and M.~J. Brett, \emph{Glancing Angle Deposition
  of Thin Films: Engineering the Nanoscale} (Wiley, 2014).

\bibitem{gfig4ref}
C.~Ungaro, A.~Shah, I.~Kravchenko, D.~K. Hensley, S.~K. Gray, and M.~C. Gupta,
  \enquote{Optical and infrared properties of glancing angle deposited
  nanostructured tungsten films,} Opt. Lett. \textbf{40}, 506--509 (2015).

\bibitem{A1}
N.~Selvakumar and H.~Barshilia, \enquote{Review of physical vapor deposited
  (pvd) spectrally selective coatings for mid- and high-temperature solar
  thermal applications,} Sol. Energy Mat. Sol. Cells \textbf{98}, 1--23 (2012).

\bibitem{A2}
C.~E. Kennedy, \enquote{Review of mid-to-high temperature solar selective
  absorber materials. technical report nrel/tp-520-31267,} Tech. rep., National
  Renew. Energ. Laboratory (2002).

\bibitem{A3}
X.~Li, Y.~Chen, J.~Miao, P.~Zhou, Y.~Zheng, and L.~Chen, \enquote{High solar
  absorption of a multilayered thin film structure,} Opt. Express \textbf{15},
  1907--1912 (2007).

\bibitem{paper1_ref7}
N.~P. Sergeant, O.~Pincon, M.~Agrawal, and P.~Peumans, \enquote{Design of
  wide-angle solar-selective absorbers using aperiodic metal-dielectric
  stacks,} Opt. Express \textbf{17}, 22800--22812 (2009).

\bibitem{stacks2}
N.~P. Sergeant, M.~Agrawal, and P.~Peumans, \enquote{High performance
  solar-selective absorbers using coated sub-wavelength gratings,} Opt. Express
  \textbf{18}, 5525--5540 (2010).

\bibitem{A4}
S.~Esposito, A.~Antonaia, M.~Addonizio, and S.~Aprea, \enquote{Fabrication and
  optimization of highly efficient cermet-based spectrally selective coatings
  for high operating temperature,} Thin Solid Films \textbf{517}, 6000--6006
  (2009).

\bibitem{A5}
L.~T. A.~Berghaus, A.~Djahanbakhsh, \enquote{Characterisation of cvd - tungsten
  – alumina cermets for high-temperature selective absorbers,} Sol. Energy
  Mat. Sol. Cells \textbf{54}, 19--26 (1998).

\bibitem{A6}
M.~Farooq and M.~Hutchins, \enquote{Optical properties of higher and lower
  refractive index composites in solar selective coatings,} Sol. Energy Mat.
  Sol. Cells \textbf{71}, 73--83 (2002).

\bibitem{A7}
D.~Xinkang, W.~Cong, W.~Tianmin, Z.~Long, C.~Buliang, and R.~Ning,
  \enquote{Microstructure and spectral selectivity of {M}o-{A}l$_2${O}$_3$
  solar selective absorbing coatings after annealing,} Thin Solid Films
  \textbf{516}, 3971--3977 (2008).

\bibitem{A8}
Q.~Zhang, Y.~Yin, and D.~Mills, \enquote{High efficiency {M}o-{A}l$_2${O}$_3$
  cermet selective surfaces for high-temperature applications,} Sol. Energy
  Mat. Sol. Cells \textbf{40}, 43--53 (1996).

\bibitem{A9}
Q.~Zhang, \enquote{Recent progress in high-temperature solar selective
  coatings,} Sol. Energy Mat. Sol. Cells \textbf{62}, 63--74 (2000).

\bibitem{A10}
R.~Schmidt and K.~Park, \enquote{High-temperature space-stable selective solar
  absorber coatings,} Appl. Opt. \textbf{4}, 917--925 (1965).

\bibitem{Therm_stabil_W_microstructures}
C.~Schlemmer, J.~Aschaber, V.~Boerner, and J.~Luther, \enquote{Thermal
  stability of micro-structured selective tungsten emitters,}
  Thermophotovoltaic Generation of Electricity: 5th Conference, CP653 -
  American Institute of Physics  (2003).

\bibitem{photonic_crystal_rev}
V.~Rinnerbauer, S.~Ndao, Y.~X. Yeng, W.~R. Chan, J.~J. Senkevich, J.~D.
  Joannopoulos, M.~Soljacic, and I.~Celanovic, \enquote{Recent developments in
  high-temperature photonic crystals for energy conversion,} Energy and
  Environmental Science  (2012).

\bibitem{A19}
F.~Ghmari, T.~Ghbara, M.~Laroche, R.~Carminati, and J.-J. Greffet,
  \enquote{Influence of microroughness on emissivity,} Journal of Applied
  Physics \textbf{96}, 2656--2664 (2004).

\bibitem{A14}
A.~Lasagni, M.~Nejati, R.~Clasen, and F.~Mucklich, \enquote{Periodical surface
  structuring of metals by laser interference metallurgy as a new fabrication
  method of textured solar selective absorbers,} Adv. Eng. Mater. \textbf{8},
  580--584 (2006).

\bibitem{convection}
M.~Saidi and R.~H. Abardeh, \enquote{Air pressure dependence of
  natural-convection heat transfer,} Proceedings of the World Congress on
  Engineering 2010 \textbf{II} (2010).

>>>>

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]
\usepackage{opex3}
\usepackage{color}
\usepackage{amsmath}
%%%%%%%%%%%%%%%%%%%%%
% REMOVE BEFORE SUBMISSION
\usepackage{amsmath,amssymb,graphicx}
\usepackage{dcolumn}%
\usepackage{array,multirow}
\usepackage{bm}%
%\usepackage{cite}
\usepackage{pstool}%
\usepackage{array}
\usepackage{xcolor}
\usepackage{subcaption,subfloat} % lets you have multiple pictures next to each other
%\usepackage{upgreek}
%\usepackage[numbers,sort&compress]{natbib}
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{A\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{A\arabic{figure}}%
     }
\journal{Solar Energy Materials and Solar Cells}
\bibliographystyle{elsarticle-num}

\begin{document}
\begin{frontmatter}
\title{Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion } %Title of paper

\author{Mool C. Gupta,$^{1,*}$ Craig Ungaro,$^1$ 
Jonathan J. Foley IV,$^{2}$ and Stephen K. Gray$^{3,\dagger}$}

\address{$^1$Department of Electrical \& Computer Engineering, University of Virginia, Charlottesville, Virginia, 22901, USA \\
$^2$Department of Chemistry, William Paterson University, 300 Pompton Road, Wayne, NJ, 07470, USA \\
$^3$Center for Nanoscale Materials, Argonne National Laboratory, 9700 South Cass Avenue, Argonne, IL, 60439, USA \\
$^*$mgupta@virginia.edu \\
$^{\dagger}$gray@anl.gov}

@@

\begin{keyword}
\ocis{(220.022) Optical design and fabrication; (230.023) Optical devices;  (240.024) Optics at surfaces; (240.031) Thin films; (350.605) Solar Energy; (310.662) Subwavelength structures, nanostructures.}
\end{keyword}

\end{frontmatter}
%\ocis{350.6050}% REPLACE WITH CORRECT OCIS CODES FOR YOUR ARTICLE
%                          % NOTE: \ocis{} IS ALIASED TO \pacs{} BUT MUST
%                          % FORMAT THE TERMS CORRECTLY FOR EACH JOURNAL

%%%\maketitle %% required
\linenumbers

\providecommand{\noopsort}[1]{}\providecommand{\singleletter}[1]{#1}%

\section{Introduction}
Recently, there has been strong research activity in solar thermal (ST) \cite{g1,g2}, solar thermophotovoltaic (STPV) \cite{g3,g4,g5,nnn1}, and thermophotovoltaic (TPV) \cite{g6,g7} energy conversion.  To provide a state of the art status in 
these fields, we have prepared this review article.  There is strong potential for growth in these areas, especially 
through the use of novel nanostructured surfaces to control light absorption and emission from surfaces and to 
achieve high efficiency. This spectral light control can be achieved by nanostructuring of surfaces, 
which can strongly modify their optical properties \cite{g8,g9,RF_OptExp_2009}. Recently, significant progress has been made in the modeling and fabrication of nanostructures to control optical absorption and emission properties of surfaces. 
Nanostructured surfaces, for example, can be designed to be significantly
more absorbing than their flat counterparts.
Similarly, surfaces can be designed to emit infrared radiation in a very narrow spectral range, providing spectrally selective 
surfaces~\cite{G_PS_1985, C_RPP_2014}.  Figure \ref{gfig_bbs} shows the change in 
emission spectra from a blackbody emitter to a selective emitter using optical nanostructures.
Some typical nanostructures are depicted schematically in Fig. \ref{gfig_surfs}.
